---
title: "Nachiket Nareshkumar Pasrija (000918216)"
subtitle: "Predictive Data Analytics (DATA-420-A)"
output:
  html_document:
    df_print: paged
---
<style>
body {
text-align: justify}
</style>

### __Assignement 5__

```{r,message=FALSE}
library(tidyverse)
library(factoextra)
library(tidyr)
```

#### __1. Load the dataset mammal_Sleep.csv into a data frame.__
```{r,message=FALSE}
mammal <- read.csv("~/mammal_Sleep.csv", header = TRUE)
```
<br>

#### __2. Create a new data frame mammalSleep with sleep_total and sleep_rem.__
```{r,message=FALSE}
mammalSleep <- mammal[, c("sleep_total", "sleep_rem")]
mammalSleep

#Checking and Cleaning Data to perform k-means clustering without error
any(is.na(mammalSleep))
mammalSleep <- na.omit(mammalSleep)
```
<br>

#### __3.Fit a k-means clustering model with 4 clusters to the data subset mammalSleep.__
```{r,message=FALSE}
clusters <- 4  

kc_model <- kmeans(mammalSleep, centers = clusters)
kc_model

cluster_assignments <- kc_model$cluster

mammalSleep_with_clusters <- cbind(mammalSleep, Cluster = cluster_assignments)
mammalSleep_with_clusters

```

Here, we specify the use of four clusters as a requirement. We then apply the __`kmeans()`__ function to perform k-means clustering on the cleaned mammalSleep dataset, specifying four clusters using the 'centers' parameter. The cluster assignments are extracted from the model using __`kmeans_model$cluster`__ and added to a new data frame named __`mammalSleep_with_clusters`__.

<br>

#### __4. Find the centroids of the clusters in the model on the chart (If you can’t figure how to it using fviz_cluster function, you can use plot() or geom_point().__

```{r,message=FALSE}
centroids <- fviz_cluster(kc_model, data = mammalSleep, geom = "point", 
                          show.clust.cent = TRUE, 
                          palette = c("red", "blue", "darkorange", "darkgreen"))

centroids + ggtitle("K-Means Clustering of Mammal Sleep Data") +
            xlab("Sleep Total") +
            ylab("Sleep REM")
```

